|

### 2021-08-16 article/article.Rmd
Distribution of Seats Graph

\begin{figure}[htb!]
  \begin{center}
    \begin{minipage}{1 \linewidth}
      \centerline{\includegraphics[width=6in,angle=0]{figs/distrseats2019.pdf}}
      \caption{Distribution of Municipalities by Population and City Council Size XXXX CHANGE HERE}
      \bigskip
      \label{fig:runningvarplot}
    \end{minipage}
  \end{center}
\end{figure}

>>>>

\begin{figure}[htb!]
  \begin{center}
    \begin{minipage}{1 \linewidth}
      \centerline{\includegraphics[width=6in,angle=0]{../figures/distrSeats.pdf}}
      \caption{Distribution of Municipalities by Population and City Council Size}
      \bigskip
      \label{fig:runningvarplot}
    \end{minipage}
  \end{center}
\end{figure}
